---
title: "eq_sim confronts sam and sep"
author: "Einar Hjörleifsson"
date: "17 July 2017"
output:
  html_document: 
    fig_height: 6
    fig_width: 9
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```


```{r}
library(FLCore)
library(msy)
library(cowplot)
library(tidyverse)
theme_set(theme_gray())
source("R/functions/rbx_to_flr.R")
source("R/functions/eqsr_tidy.R")
source("R/functions/eqsr_tidy_plot.R")
```

## Preamble

This is work in progress ...

At the webex 2017-07-17 is was considered of some value to run the stock-recruitment pairs from sam vs sep models through the eqsim part of the msy-package machinery.

## The eqsr_fit part

Here ran both framework results through the stock recruitment part of the msy. Used three diffferent year ranges:

* 1980-2015: the full time series
* 1990-2015: the time period run at wkwide
* 1980-2013: full time series but dropping off the most recent years (where uncertainty in the data is greater)

In all cases allowed only Beverton and Segmented regreg models (that being done at wkwide)

Below is the code and a pairwise results (sam0 is the wkwide final run, sep is husky's current preferred run):

```{r, eval = FALSE}
# ------------------------------------------------------------------------------
# STUFF NOT RUN, see saved object at bottom of chunk

# ------------------------------------------------------------------------------
# separable model
rbx <-
  fishvice::read_separ("/net/hafkaldi/export/u2/reikn/hoski/Mackerel/HCRSimulations/2periods/",
                       "HockeyAcf00",
                       run = "HockeyEstAcf",
                       mName = "sep")


rbya <- 
  rbx$rbya %>% 
  as_tibble() %>% 
  filter(year <= 2016)
# NOTE: need the right pF and pM
rbya$dW <- rbya$lW <- rbya$pF <- rbya$pM <- 0
# put input in first columns, then n then the rest
rbya <-
  rbya %>% 
  select(year:sW, mat, m, f, pM:dW, n, ssbW, z, f, pC:assYear) %>% 
  mutate(n = n * 1e3)
rby <- 
  rbx$rby %>% 
  as_tibble() %>% 
  mutate(r = r * 1e6,
         ssb = ssb * 1e6,
         oY = oY * 1e3) %>% 
  filter(year <= 2016)
rbx <- list(rby = rby, rbya = rbya)

flr <- 
  rbx %>% 
  rbx_to_flr()

sr.fit <- sr.tidy <- sr.plot <-  list()
cntr <-
  list(yr = list(c(1980:2015), c(1990:2015), c(1980:2013)),
       name = list("sep 1980:2015", "sep 1990:2015", "sep 1980:2013"))

for (i in 1:length(cntr[[1]])) {

  sr.fit[[i]] <-
    flr %>%
    FLCore::trim(year = cntr$yr[[i]]) %>%
    eqsr_fit(nsamp = 2500, models = c("Bevholt", "Segreg"))
  sr.tidy[[i]] <-
    sr.fit[[i]] %>%
    eqsr_tidy(Scale = 1e6, name = cntr$name[[i]])
  sr.plot[[i]] <-
    sr.tidy[[i]] %>%
    eqsr_tidy_plot(n = 2e4) +
    labs(title = cntr$name[[i]]) +
    coord_cartesian(xlim = c(0, 5.1), ylim = c(0, 10.5)) +
    scale_x_continuous(breaks = seq(0, 5, by = 0.5)) +
    scale_y_continuous(breaks = 1:11)

}

sr.sep <- list(sr.fit = sr.fit, sr.tidy = sr.tidy, sr.plot = sr.plot)

# ------------------------------------------------------------------------------
# sam
attach("ass/wkwide/eqSim_res2016.RData")

sr.fit <- sr.tidy <- sr.plot <-  list()
cntr <-
  list(yr = list(c(1980:2015), c(1990:2015), c(1980:2013)),
       name = list("sam0 1980:2015", "sam0 1990:2015", "sam0 1980:2013"))

for (i in 1:length(cntr[[1]])) {

  sr.fit[[i]] <-
    Mac %>%
    FLCore::trim(year = cntr$yr[[i]]) %>%
    msy::eqsr_fit(nsamp = 2500, models = c("Bevholt", "Segreg"))
  sr.tidy[[i]] <-
    sr.fit[[i]] %>%
    eqsr_tidy(Scale = 1e6, name = cntr$name[[i]])
  sr.plot[[i]] <-
    sr.tidy[[i]] %>%
    eqsr_tidy_plot(n = 2e4) +
    labs(title = cntr$name[[i]]) +
    coord_cartesian(xlim = c(0, 5.1), ylim = c(0, 10.5)) +
    scale_x_continuous(breaks = seq(0, 5, by = 0.5)) +
    scale_y_continuous(breaks = 1:11)

}
sr.sam0 <- list(sr.fit = sr.fit, sr.tidy = sr.tidy, sr.plot = sr.plot)

# ------------------------------------------------------------------------------
# save stuff
save(sr.sep, sr.sam0, file = "data/sr_sam_sep.rda")
```


```{r}
load("data/sr_sam_sep.rda")
plot_grid(sr.sam0$sr.plot[[2]], sr.sep$sr.plot[[2]], ncol = 2)
plot_grid(sr.sam0$sr.plot[[1]], sr.sep$sr.plot[[1]], ncol = 2)
plot_grid(sr.sam0$sr.plot[[3]], sr.sep$sr.plot[[3]], ncol = 2)
```

## The eqsim part

For now only ran the year range used at wkwide (1990 - 2015)

```{r, eval = FALSE}
sim.sam0 <- eqsim_run(sr.sam0$sr.fit[[2]], 
                      bio.years = c(2011, 2015), 
                      bio.const = FALSE,
                      sel.years = c(2006, 2015),  
                      sel.const = FALSE, 
                      Fscan = seq(0.01,0.8 , len = 80), 
                      Fcv = 0.35,
                      Fphi = 0.61,
                      SSBcv = 0.31,
                      rhologRec = F, 
                      Blim=1940000,
                      Bpa=2570000,
                      Btrigger = 0, #2570000,
                      Nrun = 100, 
                      process.error = TRUE, 
                      verbose = TRUE)
sim.sep <- eqsim_run(sr.sep$sr.fit[[2]], 
                      bio.years = c(2011, 2015), 
                      bio.const = FALSE,
                      sel.years = c(2006, 2015),  
                      sel.const = FALSE, 
                      Fscan = seq(0.01,0.8 , len = 80), 
                      Fcv = 0.35,
                      Fphi = 0.61,
                      SSBcv = 0.31,
                      rhologRec = F, 
                      Blim=1940000,
                      Bpa=2570000,
                      Btrigger = 0, #2570000,
                      Nrun = 100, 
                      process.error = TRUE, 
                      verbose = TRUE)
save(sim.sam0, sim.sep, file = "data/sim_tmp.rda")
```

```{r}
load("data/sim_tmp.rda")
```

**The sam results** (a repeat of wkwide):

```{r}
eqsim_plot(sim.sam0)
sim.sam0$Refs
```


**The sep results**:
```{r}
eqsim_plot(sim.sep)
sim.sep$Refs
```

