---
title: "hcr summary table - base run"
output: 
  html_document: 
    code_folding: hide
    fig_height: 6
    fig_width: 9
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r}
Blim <- 1.94
Bpa <- 2.57
library(tidyverse)

root <- "/net/hafkaldi/export/u2/reikn/hoski/Mackerel/HCRSimulations/2periods"
runs <- c("BevHEstAcf",
          "HockeyEstAcf",
          "RickerEstAcf",
          "HockeyEstAcfdensdepnotrend",
          "BevHEstAcfdensdepnotrend",
          "HockeyEstAcfdensdepTrend",
          "BevHEstAcfdensdepTrend")
default <- "HockeyEstAcf"
```


```{r, eval = FALSE}
load(paste0(root, "/", default, "/", "HCRrunresponse.rdata"))
d <-
  alldata %>%
  select(Btrigger, Meanwtyears, FishingMortality, MaxChange, year:refbio) %>%
  gather(variable, value, catch:refbio) %>%
  mutate(value = ifelse(variable != "refF", value/1e3, value),
         value = ifelse(variable == "n1", value/1e3, value)) %>%
  group_by(Btrigger, Meanwtyears, FishingMortality, MaxChange, year, variable) %>%
  summarise(q05 = quantile(value, 0.05),
            q25 = quantile(value, 0.25),
            q50 = quantile(value, 0.50),
            m = mean(value),
            q75 = quantile(value, 0.75),
            q95 = quantile(value, 0.95)) %>%
  ungroup()

probs <-
  alldata %>%
  select(Btrigger, Meanwtyears, FishingMortality, MaxChange, year, ssb) %>%
  group_by(Btrigger, Meanwtyears, FishingMortality, MaxChange, year) %>%
  summarise(n = n(),
            pBlim = sum(ssb < Blim * 1e3) / n,
            pBpa  = sum(ssb < Bpa * 1e3)  / n,
            pBtrigger = sum(ssb < Btrigger) / n) %>%
  ungroup()
save(d, probs, file = "data/hcr_summary_default.rda")
```

```{r}
load("data/hcr_summary_default.rda")
pBlim <-
  probs %>%
  select(Btrigger:year, q50 = pBlim) %>%
  mutate(variable = "pBlim") %>%
  filter(year > 2014)
d2 <-
  d %>%
  bind_rows(pBlim)

dummy <- 
  data_frame(variable = c("ssb", "pBlim"),
             lim = c(Blim, 0.05)) %>%
  mutate(variablef = factor(variable, levels = c("ssb", "pBlim")))

d2 %>%
  filter(variable %in% c("catch", "ssb", "refF", "pBlim"),
         Btrigger == 600,
         Meanwtyears == 5,
         MaxChange == 3,
         FishingMortality %in% c(0.18, 0.19, 0.20, 0.22, 0.25, 0.30, 0.35)) %>%
  mutate(variablef = factor(variable, levels=c('ssb','catch','refF','pBlim'))) %>%
  ggplot(aes(year)) +
  geom_vline(xintercept = 2015) +
  geom_hline(data = dummy, aes(yintercept = lim)) +
  geom_ribbon(aes(ymin = q05, ymax = q95), fill = "red", alpha = 0.25) +
  geom_ribbon(aes(ymin = q25, ymax = q75), fill = "red", alpha = 0.25) +
  geom_line(aes(y = q50)) +
  facet_grid(variablef ~ FishingMortality, scale = "free_y") +
  expand_limits(y = 0) +
  labs(title = "Default run, no trigger (value used 600kt), no buffer, weights last 5 years",
       subtitle = "Data show q05, q25, median, q75 and q95")
```

In the tables below we have 4 variables:

* MaxChange: The catch stabilizer, if 3 then effectively this means no catch stabilizer
* term: The time period
    - LT: 2033-2085
    - MT: 2023-2032
    - ST: 2018:2022
* Btrigger: Here the lowest value is 600 kt, set because a value of 40 kt resulted in crashing under some scenarios. Effectively the lowest value is equivalent to no Btrigger under likely fishing mortality multipliers.
* Meanwtyears
    - 5: Mean weights last 5 years
    - 20: Mean weights last 20 years


```{r}
# We need to evaluate short-term (ST), medium-term (MT) and long-term (LT)
# (2018-2022), medium term (2023-2032) and long term (2033-2052)
terms <- data_frame(year = 2018:2052,
                    term = ifelse(year %in% 2018:2022, "ST",
                                  ifelse(year %in% 2023:2032, "MT", "LT")))
ptable <-
  probs %>%
  left_join(terms) %>%
  filter(!is.na(term),
         FishingMortality < 0.36) %>%
  group_by(MaxChange, term, Btrigger, Meanwtyears, FishingMortality) %>%
  summarise(pBlim = round(max(pBlim) * 100, 1)) %>%
  ungroup() %>%
  #filter(term == "LT") %>%
  spread(FishingMortality, pBlim) %>%
  arrange(desc(MaxChange), term, Meanwtyears, Btrigger)
ptable %>%
  knitr::kable(caption = "Probability of ssb going below Blim")
d3 <-
  d2 %>%
  left_join(terms) %>% 
  filter(!is.na(term)) %>% 
  group_by(MaxChange, term, Btrigger, Meanwtyears, FishingMortality, variable) %>% 
  # Not sure if one should take the mean of the medians??
  summarise(median = mean(q50))
d3 %>% 
  filter(variable == "catch",
         FishingMortality < 0.36) %>% 
  select(-variable) %>% 
  mutate(median = round(median, 3)) %>% 
  spread(FishingMortality, median) %>% 
  arrange(desc(MaxChange), term, Meanwtyears, Btrigger) %>% 
  knitr::kable(caption = "Median catch")
d3 %>% 
  filter(variable == "ssb",
         FishingMortality < 0.36) %>% 
  select(-variable) %>% 
  mutate(median = round(median, 3)) %>% 
  spread(FishingMortality, median) %>% 
  arrange(desc(MaxChange), term, Meanwtyears, Btrigger) %>% 
  knitr::kable(caption = "Median ssb")
```

```{r, eval = FALSE, echo = FALSE}
# NOT RUN
basedir <- "/net/hafkaldi/export/u2/reikn/hoski/Mackerel"
subdirs <- c("HockeyAcf0008PinFile",
             "HockeyAcf0008PinFilemcrb2",
             "HockeyAcf0012PinFile",
             "HockeyAcf0012PinFilemcrb2",
             "HockeyAcf00sqrt08PinFile",
             "HockeyAcf00sqrt12PinFile",
             "HockeyAcf00sqrt12PinFilemcrb02",
             "HockeyAcf00FixedSSBBreak")
txt <- c("log, low lim 800","log, low lim 800 mcrb2","log, low lim 1200","log, low lim 1200 mcrb 2","sqrt, low lim 800","sqrt low lim 1200", "sqrt low lim 1200 mcrb2","SSBbreak fixed at 2000")
sumdata1 <- sumdata2 <- data.frame()
for(i in 1:length(subdirs)){
  load(paste(basedir,"HCRSimulations/Final",subdirs[i],"HCRrunsum.rdata",sep="/"))
  sumdata$run <- txt[i]
  sumdata20 <- sumdata[sumdata$Meanwtyears==20 & sumdata$Btrigger < 50,]
  sumdata5 <- sumdata[sumdata$Meanwtyears==5 & sumdata$Btrigger < 50,]
  sumdata1 <- rbind(sumdata1,sumdata20)
  sumdata2 <- rbind(sumdata2,sumdata5)
}
ggplot(sumdata2, aes(FishingMortality, catchmean, col = run)) +
  geom_vline(xintercept=seq(0.16,0.3,by=0.02),col="lightgrey") +
  geom_line(lwd=2)+theme_bw() +
  scale_colour_brewer(palette = "Set1") +
  theme(legend.position=c(0.8,0.75))
ggplot(sumdata2,aes(FishingMortality,catchmed,col=run)) +
  theme_bw()+
  geom_vline(xintercept=seq(0.16,0.3,by=0.02),col="lightgrey")+
  geom_line(lwd=2)+
  scale_colour_brewer(palette = "Set1") +
  theme(legend.position=c(0.4,0.4))
ggplot(sumdata2,aes(FishingMortality,ssb05,col=run))+
  theme_bw()+
  geom_vline(xintercept=seq(0.16,0.3,by=0.02),col="lightgrey")+
  geom_line(lwd=1)+
  scale_colour_brewer(palette = "Set1") +
  theme(legend.position=c(0.8,0.7))+
  geom_abline(intercept = 1840,lwd=2) +
  ylab("1000 tonnes")
#load("/net/hafkaldi/export/u2/reikn/hoski/Mackerel/HCRSimulations/Final/HockeyAcf0012PinFilemcrb2/HCRrunsum.rdata")
```

